PANCHANGE_data_preprocessing

### 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd

```{r coping ramp gad cleaning}
if(RAMP == TRUE) {
  exclude_cols_ramp <- c(
    "Sample",
    "ID",
    "startDate.ramp"
  )

  ramp.gad.raw.id <- ramp.gad.raw %>%
    drop_na(`Login ID`) %>% # Drop NAs
    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)
    ) %>% 
    select(
      Sample, # Sample
      ID, # ID
      startDate.ramp = startDate, # Rename startDate
      gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
      gad.pandemic_felt_feelings = gad.feelings_pandemic_felt, # Comparison to before the pandemic (retro)
      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge.1, #retro and baseline coding are reversed for RAMP
      gad.control_worrying_stop_retro = gad.control_worrying_stop.1, #.1 = retro
      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things.1,
      gad.trouble_relaxing_retro = gad.trouble_relaxing.1,
      gad.sit_restless_hard_retro = gad.sit_hard_restless.1,
      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable.1,
      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen.1,
      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge,
      gad.control_worrying_stop_base = gad.control_worrying_stop,
      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things,
      gad.trouble_relaxing_base = gad.trouble_relaxing,
      gad.sit_restless_hard_base = gad.sit_hard_restless,
      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable,
      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen
    ) %>%
    add_numeric(., exclude = exclude_cols_ramp) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

```{r coping ramp gad cleaning}
if(RAMP == TRUE) {
  exclude_cols_ramp <- c(
    "Sample",
    "ID",
    "startDate.coping"
  )

  ramp.gad.raw.id <- ramp.gad.raw %>%
    drop_na(`Login ID`) %>% # Drop NAs
    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)
    ) %>% 
    select(
      Sample, # Sample
      ID, # ID
      startDate.coping = startDate, # Rename startDate
      gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
      gad.pandemic_felt_feelings = gad.feelings_pandemic_felt, # Comparison to before the pandemic (retro)
      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge.1, #retro and baseline coding are reversed for RAMP
      gad.control_worrying_stop_retro = gad.control_worrying_stop.1, #.1 = retro
      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things.1,
      gad.trouble_relaxing_retro = gad.trouble_relaxing.1,
      gad.sit_restless_hard_retro = gad.sit_hard_restless.1,
      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable.1,
      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen.1,
      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge,
      gad.control_worrying_stop_base = gad.control_worrying_stop,
      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things,
      gad.trouble_relaxing_base = gad.trouble_relaxing,
      gad.sit_restless_hard_base = gad.sit_hard_restless,
      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable,
      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen
    ) %>%
    add_numeric(., exclude = exclude_cols_ramp) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
